The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow

### 2016-10-03 paper/thingap_mri_paper.tex
added linear dispersion relation. note that our growth rate dependence is quartic

\begin{align}
\mathcal{O}(\epsilon)&: \mathcal{L}\mathbf{V_1} + \mathcal{D}\partial_t \mathbf{V_1} = 0. \\ \label{eq:ordere}
\mathcal{O}(\epsilon^2)&: \mathcal{L}\mathbf{V_2} + \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1} = \mathbf{N_2}\\
\mathcal{O}(\epsilon^3)&: \mathcal{L} \mathbf{V_3} + \mathcal{D}\partial_T \mathbf{V_1}  + \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} + \widetilde{\mathcal{G}}\mathbf{V_1} = \mathbf{N_3} \, \\ \label{eq:ordere3}
\end{align}

@@

The fact that we find a Ginzburg-Landau equation for the amplitude is unsurprising: such an amplitude equation can be found in any system with Euclidean symmetry and a quadratic maximum in growth rate with respect to $k$ \citep{Hoyle:2006}. In this case, the Euclidean symmetry comes from axisymmetry in the $x$-$z$ plane.  In Paper II, we show that the same symmetry occurs in the axisymmetric global geometry as well. Figure~\ref{fig:u_saturation} shows the saturated mean radial profiles of $u_0 - u_{\phi} = -q \Omega_0 x - u_{\phi}$ and each term in the steady state force balance (i.e. equation~(\ref{eqset2} with $\partial_t u_{1y} = 0$). In the bulk of the fluid away from the boundary layers, the saturated state shows reduced shear, with little diffusive contribution. However, the steep scaling of transport with $\Pm$

@@

\section{A. Detailed Equations}\label{app:matrices}

Here we detail the perturbation analysis described in Section \ref{sec:equations}. The linear system is described by Equation \ref{eq:unperturbed_matrix_eqns}, where

@@

\section{B. Expansion of Nonlinear Terms}\label{app:nonlinear_terms}
\beq
\mathbf{N} = \epsilon^2\mathbf{N_2} \, + \, \epsilon^3\mathbf{N_3} \, + \, \mathcal{O}(\epsilon^4)
\eeq

>>>>

\begin{align}
\mathcal{O}(\epsilon)&: \mathcal{L}\mathbf{V_1} + \mathcal{D}\partial_t \mathbf{V_1} = 0. \label{eq:ordere}\\
\mathcal{O}(\epsilon^2)&: \mathcal{L}\mathbf{V_2} + \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1} = \mathbf{N_2} \label{eq:ordere2}\\
\mathcal{O}(\epsilon^3)&: \mathcal{L} \mathbf{V_3} + \mathcal{D}\partial_T \mathbf{V_1}  + \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} + \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} + \widetilde{\mathcal{G}}\mathbf{V_1} = \mathbf{N_3} \label{eq:ordere3}
\end{align}

@@

The fact that we find a Ginzburg-Landau equation for the amplitude is unsurprising: such an amplitude equation can be found in any system with Euclidean symmetry and a quadratic (or in our case quartic) maximum in growth rate with respect to $k$ \citep{Hoyle:2006}. In this case, the Euclidean symmetry comes from axisymmetry in the $x$-$z$ plane.  In Paper II, we show that the same symmetry occurs in the axisymmetric global geometry as well. Figure~\ref{fig:u_saturation} shows the saturated mean radial profiles of $u_0 - u_{\phi} = -q \Omega_0 x - u_{\phi}$ and each term in the steady state force balance (i.e. equation~(\ref{eqset2} with $\partial_t u_{1y} = 0$). In the bulk of the fluid away from the boundary layers, the saturated state shows reduced shear, with little diffusive contribution. However, the steep scaling of transport with $\Pm$

@@

\section{A. Linear dispersion relation}\label{app:dispersion}

The linear dispersion relation, which determines the variable scalings in the multiple scales analysis. This relation is found by perturbing the linear system (Equation \ref{eq:ordere}) with a small perturbation of the form $e^{\sigma t + i k_x x + i k_z z}$.

\beq
\begin{split}
& \frac{B_{0}^{4} k_{x}^{2} k_{z}^{4}}{16 \pi^{2}} + \frac{B_{0}^{4} k_{z}^{6}}{16 \pi^{2}} - \frac{B_{0}^{2} \Omega_{0} k_{z}^{4} q}{2 \pi} - 2 \Omega_{0} k_{z}^{2} q \sigma^{2} - \frac{4 \sigma}{\reym} \Omega_{0} k_{x}^{2} k_{z}^{2} q - \frac{4 \sigma}{\reym} \Omega_{0} k_{z}^{4} q - \frac{2 \Omega_{0}}{\reym^{2}} k_{x}^{4} k_{z}^{2} q - \frac{4 \Omega_{0}}{\reym^{2}} k_{x}^{2} k_{z}^{4} q - \frac{2 \Omega_{0}}{\reym^{2}} k_{z}^{6} q \\
& - k_{x}^{2} \sigma^{4} - k_{z}^{2} \sigma^{4} + 4 k_{z}^{2} \sigma^{2} - \frac{2 \sigma^{3}}{\reym} k_{x}^{4} - \frac{4 \sigma^{3}}{\reym} k_{x}^{2} k_{z}^{2} + \frac{8 \sigma}{\reym} k_{x}^{2} k_{z}^{2} - \frac{2 \sigma^{3}}{\reym} k_{z}^{4} + \frac{8 \sigma}{\reym} k_{z}^{4} - \frac{k_{x}^{6} \sigma^{2}}{\reym^{2}} - \frac{3 \sigma^{2}}{\reym^{2}} k_{x}^{4} k_{z}^{2} + \frac{4 k_{x}^{4}}{\reym^{2}} k_{z}^{2} \\
& - \frac{3 \sigma^{2}}{\reym^{2}} k_{x}^{2} k_{z}^{4} + \frac{8 k_{x}^{2}}{\reym^{2}} k_{z}^{4} - \frac{k_{z}^{6} \sigma^{2}}{\reym^{2}} + \frac{4 k_{z}^{6}}{\reym^{2}} - \frac{2 \sigma^{3}}{\reye} k_{x}^{4} - \frac{4 \sigma^{3}}{\reye} k_{x}^{2} k_{z}^{2} - \frac{2 \sigma^{3}}{\reye} k_{z}^{4} - \frac{4 k_{x}^{6} \sigma^{2}}{\reye \reym} -  \frac{12 k_{x}^{4} k_{z}^{2} \sigma^{2}}{\reye \reym} - \frac{12 k_{x}^{2} k_{z}^{4} \sigma^{2}}{\reye \reym} \\
& - \frac{4 k_{z}^{6} \sigma^{2}}{\reye \reym} - \frac{2 k_{x}^{8} \sigma}{\reye \reym^{2}} - \frac{8 k_{x}^{6} k_{z}^{2} \sigma}{\reye \reym^{2}} - \frac{12 k_{x}^{4} k_{z}^{4} \sigma}{\reye \reym^{2}} - \frac{8 k_{x}^{2} k_{z}^{6} \sigma}{\reye \reym^{2}} - \frac{2 k_{z}^{8} \sigma}{\reye \reym^{2}} - \frac{k_{x}^{6} \sigma^{2}}{\reye^{2}} - \frac{3 \sigma^{2}}{\reye^{2}} k_{x}^{4} k_{z}^{2} - \frac{3 \sigma^{2}}{\reye^{2}} k_{x}^{2} k_{z}^{4} - \frac{k_{z}^{6} \sigma^{2}}{\reye^{2}} \\
& - \frac{2 k_{x}^{8} \sigma}{\reye^{2} \reym} - \frac{8 k_{x}^{6} k_{z}^{2} \sigma}{\reye^{2} \reym} - \frac{12 k_{x}^{4} k_{z}^{4} \sigma}{\reye^{2} \reym} - \frac{8 k_{x}^{2} k_{z}^{6} \sigma}{\reye^{2} \reym} - \frac{2 k_{z}^{8} \sigma}{\reye^{2} \reym} - \frac{k_{x}^{10}}{\reye^{2} \reym^{2}} - \frac{5 k_{x}^{8} k_{z}^{2}}{\reye^{2} \reym^{2}} - \frac{10 k_{x}^{6} k_{z}^{4}}{\reye^{2} \reym^{2}} - \frac{10 k_{x}^{4} k_{z}^{6}}{\reye^{2} \reym^{2}} \\
& - \frac{5 k_{x}^{2} k_{z}^{8}}{\reye^{2} \reym^{2}} - \frac{k_{z}^{10}}{\reye^{2} \reym^{2}} = 0
\end{split}
\eeq

\section{B. Detailed Equations}\label{app:matrices}

Here we detail the perturbation analysis described in Section \ref{sec:equations}. The linear system is described by Equation \ref{eq:unperturbed_matrix_equations}, where

@@

\section{C. Expansion of Nonlinear Terms}\label{app:nonlinear_terms}
\beq
\mathbf{N} = \epsilon^2\mathbf{N_2} \, + \, \epsilon^3\mathbf{N_3} \, + \, \mathcal{O}(\epsilon^4)
\eeq
